---
title: "Alzheimer Prediction - Multilevel Regression Analysis"
author: "Hao He"
date: "2022-11-30"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE,message=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
	message = FALSE,
	warning = FALSE)
library(magrittr)
library(readr)
library(tidyverse)
library(missMethods)
library(ggplot2)
library(ggcharts)
library(ggridges)
library(rstanarm)
library(arm)
library(GGally)
library(ggcorrplot)
library(kableExtra)
library(gridExtra)
library(lmerTest)
library(merTools)
library(lme4)
library(car)
library(arm)
library(AUC)
library(performance)
library(see)
library(lattice)
library(bayesplot)
```

## Abstract

Early detection of Alzheimer's Disease is essential for dementia prevention. 
The use of MRI imaging seems promising for early detection. However, with MRI 
scans, it is still hard for doctors to assess whether a patient's condition 
surely can be diagnosed with dementia at as early as possible. This analysis 
aims to figure out if it is possible to predict who has Alzheimer's by using 
the multilevel logistic model after some signs are noticed and which factor(s) 
would be influential. The result suggests that MMSE test result, age in years and
years of education are important factors.

## Introduction

Alzheimer's disease (AD), as the most common trigger of dementia among older 
people, will shrink the size of a brain and cause slow decline in memory, 
thought processes, language and functioning. After AD is diagnosed, the symptoms
gets worse, and no existing drugs in market can cure the disease. Thus, I'm 
curious about what patient factors are most related to whether a patient has 
Alzheimer's and therefore more preventive procedures could be planned for the 
future to slow down the progression of dementia. As a result, patients can 
hopefully extend their life expectancy.

The clinical data I found is longitudinal data, so it's natural to have a group 
level `patient` given each patient was scanned and measured on each visits. 
The individual-level observations including patient's social demographics and 
other clinical test results are nested within the patient - level. Since the
multilevel model is highly effective to understand the impacts of mixed effects
and make prediction, I built a multilevel logistic model to reflect the nested 
data structure and to predict if a patient has AD and how that varies between 
different patients. In this analysis, how I choose variables and modeling will 
be elaborated in Methods section. The Result section summarizes the 
interpretation of final model's results and the limitations and possible 
improvements is reported in Discussion section.

## Methods

The Longitudinal MRI Data in Nondemented and Demented Older Adults dataset in 
this analysis can be found on Kaggle, and it was originally published on the 
Open Access Series of Imaging Studies (OASIS) website as OASIS-2 [1]. In this 
dataset, 150 subjects aged from 60 to 96 are repeatedly measured over a period 
of time and information collected include group, number of visit, MR delay, 
gender, handedness, age, education, social economic status (SES), MMSE, CDR, 
eTIV, nWBV and ASF. Below is a data description for each variable [2].

+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Data       | Description                                                                                                                                                                     |
+============+=================================================================================================================================================================================+
| Subject ID | Identification of patients                                                                                                                                                      |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| MRI ID     | Identification of MRI scans                                                                                                                                                     |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Group      | Demented or Nondemented                                                                                                                                                         |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Visit      | The visit number                                                                                                                                                                |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| MR Delay   | The number of days between two medical visits                                                                                                                                   |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| M/F        | Gender                                                                                                                                                                          |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Hand       | Dominant Hand                                                                                                                                                                   |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Age        | Age in years                                                                                                                                                                    |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| EDUC       | Years of Education                                                                                                                                                              |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| SES        | Socioeconomic Status：Socioeconomic status as assessed by the Hollingshead Index of Social Position and classified into categories from 1 (highest status) to 5 (lowest status) |
|            |                                                                                                                                                                                 |
|            | 1 = upper, 2 = upper middle, 3 = middle, 4 = lower middle, 5 = lower)                                                                                                           |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| MMSE       | Mini Mental State Examination ( range from 0 (worst) to 30 (best) )                                                                                                                  |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| CDR        | Clinical Dementia Rating                                                                                                                                                        |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| eTIV       | Estimated Total Intracranial Volume                                                                                                                                             |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| nWBV       | Normalize Whole Brain Volume                                                                                                                                                    |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| ASF        | Atlas Scaling Factor                                                                                                                                                            |
+------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

```{r read data, echo=FALSE, message=FALSE}
patients <- read_csv("oasis_longitudinal.csv")
summary.p <- summary(patients, maxsum = 7,
       digits = max(3, getOption("digits")-3))

# Response variable is CDR and convert it to factor (0 = Nondemented, 1 = Demented)
patients$Response<- ifelse(patients$CDR > 0, 1, 0)

# Rename the `M/F` column with `Gender`, rename `Subject ID` column with `pid`
patients <- patients %>% rename(Gender = `M/F`) %>% rename(pid = `Subject ID` )


# colnames(patients)
 
# Find NAs for each column 
# patients %>% summarise_all((~sum(is.na(.))))
##`SES` column contains 19 NAs, `MMSE` contains 2 NAs, keep them for EDA

```

### EDA

After initial screening of data, I found there are 21 missing values in this 
dataset, I kept them for EDA part to avoid mishandling the data and miss any 
patterns. Based on the OASIS FACT SHEET [2], I knew that all participants with 
dementia (CDR \>0) were diagnosed with probable AD. Therefore, I chose `CDR` 
as the response variable for prediction of AD and converted it to a binary 
variable `Response` (0 = Nondemented, 1 = Demented). 

I plotted each variable's distribution to make sense of what variables are more 
reliable to put into my model in terms of normality. In **Figure 1** 
(see Appendix), the majority of the variables have a distribution not too far 
way from from normal distribution, however the MMSE and EDUC variable may need 
a logarithmic transformation. The MMSE variable looks left-skewed and has a 
heavy tail while EDUC has a lot of peaks.

According to the dementia status, patients are categorized into three groups,
demented, nondemented, and converted. By examining the converted group, I found 
14 patients are converted from nondemented to demented after 1 st visit, 
approximately half of them are detected with very mild dementia (see **Table 1**
in Appendix ). Since patient's visit is separated by at least one year[1], to 
reduce speculation around when these converted patients started to have AD, I 
grouped the converted and demented patients together as the demented group while
nondemented group remains the same. This is helpful to understand any potential
patterns because the outcome variable is binary.

```{r, echo=FALSE}
# check when patients changed to demented from nondemented based on CDR and summarise
converted <- patients %>% filter(Group == "Converted") %>% count(Visit,CDR)

# Convert the converted ones to demented
patients$Group <- str_replace(patients$Group,"Converted","Demented") %>% as.factor()
```

### Social-Demographics Variable

The relationship between social- demographics variable and dementia are explored
in **Figure 2** and patterns are summarized below.

```{r  warning= FALSE, fig.cap= " Figure 2. Social-Demograhpics and Dementia", echo=FALSE}
# number of patients by gender
tbl.gender<- patients %>% distinct(pid,.keep_all = T) %>% count(Gender)

# bar chart for Gender and density plot for SES, EDUC, Age 
gender.group.bar<- patients %>% distinct(pid,.keep_all = T) %>% ggplot() + aes(x=Gender, fill = Group)+ geom_bar()+ 
  geom_text(aes(label = after_stat(count)),stat = "count", colour = "white")+
  labs(title = "Gender and Dementia by Group")+ylab("Number of patient")

age.group.dens<- ggplot(patients) + aes(x=Age, fill=Group) +geom_density(alpha=0.2)+ylab("")+labs(title = "Age and Dementia by Group") + ylab("Age in years")

ses.group.dens<- ggplot(patients) + aes(x=SES, fill=Group) +geom_density(alpha=0.2)+ylab("")+labs(title = "SES and Dementia by Group")+ylab("Socioeconomic Status level") 

educ.group.dens<- ggplot(patients) + aes(x=EDUC, fill=Group) +geom_density(alpha=0.2)+ylab("")+labs(title = "EDUC and Dementia by Group")+ ylab("Years of Education")

grid.arrange(gender.group.bar, age.group.dens,ses.group.dens,educ.group.dens,ncol = 2)

```

-   `Gender` variable  The bar chart shows there are less women patients in the 
demented group, given we have 88 females and 62 males in this dataset.

-   `Age` variable  I assessed the relationship between age and dementia with my
guess being that this kind of disease starts in people's 80s and 90's. It shows 
that demented group has a higher proportion of patients aged from 65-85 than 
nondemented group. I also notice that in this dataset the nondemented group has 
more 90-year-old patients and I assume this is attributed to the fact that 
dementia reduces life expectancy.

-   `SES` variable   Demented patients tend to be in a relatively lower social 
economic status than nondemented patients, especially in the upper middle 
socioeconomic status.

-   `EDUC` variable  Demented group has more patients that are less than high 
school graduates while nondemented group has more patients that are college 
graduates and even beyond college level.

### Clinical Variable

In Figure 3, I explored all clinical variables representing brain diagnostic 
test to see how each of them is related to dementia. The takeaways from 
**Figure 3** are

-   Demented patients tend to have a higher concentration in ASF measurement 
between 1.1 and 1.25 and a higher concentration in eTIV values between 1375 and
1500. Besides, `ASF` and `eTIV` seems to be negatively related to some extent.

-   Demented patients tend to have a much lower MMSE score than nondemented 
patients. This may indicate that the lower the MMSE score, the higher the 
likelihood of patients diagnosed with Alzheimer's.

```{r echo=FALSE, warning=FALSE, fig.cap= "Figure 3. Different brain diagnostic test measurements and Dementia"}

nwbv.group.dens<- ggplot(patients) + aes(x=nWBV, fill=Group) +geom_density(alpha=0.2)+ylab("")+labs(title = "nWBV and Dementia by Group")

mmse.group.dens <- ggplot(patients) + aes(x=MMSE, fill=Group) +geom_density(alpha=0.2)+ylab("")+labs(title = "MMSE and Dementia by Group")

asf.group.dens<- ggplot(patients) + aes(x=ASF, fill=Group) +geom_density(alpha=0.2)+ylab("")+labs(title = "ASF and Dementia by Group")

etiv.group.dens<- ggplot(patients) + aes(x=eTIV, fill=Group) +geom_density(alpha=0.2)+ylab("")+labs(title = "eTIV and Dementia by Group")

grid.arrange(nwbv.group.dens, mmse.group.dens, asf.group.dens, etiv.group.dens, nrow = 2)
```

Below are some additional insights I gained about the relationship between other
predictors in this dataset indicated in **Figure 4**.

-   `SES` and `EDUC`  These two variables has a strong negative correlation 
(see **Figure 5** in Appendix) and this feature is shared in the correlation 
between `eTIV` and `ASF` variable, given 0.7 as my baseline of high correlation.
Considering this, I decided not to keep the `SES` variable in my model as it's 
more categorical and hard to interpret.

-   `eTIV` and `ASF`  There is a clear linear trend in the **Figure 4**. The 
reason why`eTIV` and `ASF` are highly correlated is that atlas normalization 
equates head size causing the ASF to be proportional to TIV [3]. I decided not 
to keep the `ASF` variable in my model.

-   `nWBV` and `Age`  In general, the older the people is, the smaller the brain
volume is. Demented patients have a smaller size of brain compared to 
nondemented patients as expected.

```{r, echo = FALSE, message=FALSE, warning=FALSE, fig.cap= "Figure 4. Correlation Matrix"}
## ggpairs assess all continuous variables
patients %>% dplyr::select(c(Age,EDUC,SES, MMSE,eTIV,nWBV,ASF))%>% ggpairs(alpha  = 0.5, cardinality_threshold = 150, title = "Correlation Matrix")

```

### Data Preprocessing

Each patient has at least two or more visits, so I kept data with total visits 
less than 3 to make sure I don't misinterpret the diagnosis and skew the data 
because my goal is trying to predict AD at a earlier time. As this dataset only 
includes 150 subject and the NAs are are Missing at Complete Random, I decided 
to impute the NAs by mean (MMSE variable) and median (SES variable) instead of 
remove them. Among all 13 variables, I removed three unnecessary columns, they 
are `MR delay`, `MRI ID`, and `Hand` because they are not informative for 
estimating dependent variable `Response`. After these steps, I got a 
294-observations dataset with 1 dependent variable `Response` and 11 predictors.

```{r data preprocessing, incldue=FALSE, echo=FALSE}

# Kepp only patients with total visits are less than 3
p1 <- patients%>% filter(Visit <3)


# remove unnecessary columns for our prediction
p1<- p1 %>% dplyr::select(-c(`MRI ID`,Hand, `MR Delay`, Visit))


# DOUBLE CHECK - if there is still missing value in p1 table
# p1 %>% summarise_all((~sum(is.na(.))))


# Imputation for missing values (as the NA is MCAR)
# Impute NA with column mean and median
p1$MMSE[is.na(p1$MMSE)] <- round(mean(p1$MMSE, na.rm = TRUE)) 
p1 <- impute_median(p1) # SES - discrete

```

### Variable Selection

Based on EDA results, I have 7 predictors for variable selection, they are 
`Gender`, `MMSE`, `EDUC`, `nWBV`, `eTIV`, and `Age`. Among them, I decide to 
only keep `MMSE`, `nWBV`, `eTIV`,`EDUC`, and `Age` as predictors. In addition, 
as I mentioned before in EDA section, MMSE has a skewed heavy-tailed 
distribution and a logarithmic transformation could help to solve this issue, 
so I transformed the `MMSE` to a log scale.

### Model Fitting

The effect of aforementioned predictors would be natural to differ by each 
patient, so I first constructed a varying-intercept multilevel as below.

```{r include=FALSE, echo=FALSE}
mod1 <- stan_glmer(Response ~ (1| pid) + Age + EDUC + log(MMSE) + nWBV + eTIV, data = p1, family = binomial(link = "logit" ), refresh = 0, seed = 678)
print(mod1, digits = 4)
```

```{r eval=FALSE}
mod1 <- stan_glmer(Response ~ (1| pid) + Age + EDUC + log(MMSE) + nWBV + eTIV, 
                   data = p1, family = binomial(link = "logit" ))
```

However, the estimated coefficient of `log(MMSE)` is -38.16 with a standards 
error of 6.45, which suggests the log transformation is not a good decision. So 
I decided to continue with `MMSE` at the original scale. I also noticed that 
`eTIV` has near zero coefficients, so I dropped the `eTIV` variable and continue
with the model below.

```{r include=FALSE, echo=FALSE}

mod2 <- stan_glmer(Response ~ (1| pid) + Age + EDUC + MMSE + nWBV, data = p1, family = binomial("logit"), refresh = 0, seed =678)
summary(mod2, digits = 4,probs = c(0.025, 0.975))

```

```{r eval=FALSE}
mod2 <- stan_glmer(Response ~  Age + EDUC + MMSE + nWBV+ (1| pid), data = p1, 
                   family = binomial("logit"))

```

With the standard error of `nWBV` being 16.5 based on the model summary in 
Appendix, it is impossible to claim that `nWBV` is an important factor for 
prediction. And the reason of this big standard error is probably because `nWBV`
is correlated with Age and MMSE.

But the rest of the variables still seems important in the same way. So the 
final model and its summary is as below. 

```{r,eval=FALSE}
mod3 <- stan_glmer(Response ~ (1| pid) + Age + EDUC + MMSE, data = p1, 
                   family = binomial(link = "logit" ))
```

```{r echo=FALSE}

mod3 <- stan_glmer(Response ~ (1| pid) + Age + EDUC + MMSE, data = p1, family = binomial(link = "logit" ), refresh = 0,  seed = 678)
# summary(mod3,digits = 4, probs = c(0.025, 0.975))

print(mod3, digits = 4)

```

Below is the first 6 random effects parameters of patients.
```{r, echo=FALSE, fig.cap= "Final model - First 5 random effects parameters", }
round(ranef(mod3)$pid,digits = 2) %>% head()
```

## Result

### Interpretation

The interpretation of the this model needs to fix the varying effect - patient, 
which means the coefficients can be only interpreted as odds ratio when the 
patient is the same. 

The interpretation of fixed effects here should be similar to logistic model. 
For example, for `Age`, a one unit increase in years of age is associated with 
a 0.05 unit decrease in the expected log odds of having Alzheimer's. It may 
seems not straightforward at the first glance, so I transformed the estimate to 
a odds ratio. The odds ratio here is the conditional odds ratio for a patient 
holding `EDUC` and `MMSE` constant as well as for a patient with the same 
doctor, or doctors with identical random effects. The exponent of 0.05 is 
greater than 1, it indicates that as the age of a patient increases the 
predicted probability of a patient is diagnosed is lower than a patient is 
nondemented. This contradicts with our findings in EDA, this may suggest the 
collinearity exist.

For `EDUC`, a one unit increase in years of education is associated with a 0.28 
unit decrease in the expected log odds of having Alzheimer's. It can also be 
interpreted qualitatively that people who are less educated are expected to have
higher log odds of being diagnosed with Alzheimer's than people who are 
well-educated. For `MMSE`, a one unit increase in `MMSE` score is associated 
with a 1.4 unit decrease in the expected log odds of having Alzheimer.

### Model Checking

Below is the posterior density check plots, it indicates the model fit is okay 
with acceptable variations compared to the observed data we have. 

```{r echo = FALSE, fig.height = 4, fig.cap= " Figure 6. Posterior Predictive Check"}
mod3pred <- posterior_predict(mod3) 

ppc_dens_overlay(p1$Response,mod3pred[1:100,])
```

However, the are some issues with model checking. Figure 7 below indicates the 
checking on normality, collinearity, residuals and outliers of this model. The 
normality seems acceptable although there are some points on tail and head falls
off the line and this may be attributed to the outliers shown in the influence 
plot which is above the Q-Q plot. Also, based on the residuals, we know that the
predictive performance at the most of time is okay but with relatively lower 
predictive accuracy. Furthermore, it is normal to see collinearity happens 
because this is a longitudinal data and the Alzheimer's is closely related with 
age.

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.pos = 'h', fig.height = 8, fig.width =7.5, fig.cap = "Figure 7. model check"}
# model checking
performance::check_model(mod3)
```

## Discussion

In this analysis, I built a multilevel logistic model to predict if a patient 
has Alzheimer's using three influential predictors, `Age`, `EDUC`, `MMSE`. I 
didn't consider any interaction term here given it's rank deficient if I only 
stick to the three individual-level predictors in the final model. This would 
make the random effects unidentifiable. I was able to figure out the overall 
negative relationship between my predictors and the dependent variable. 

This analysis do have several limitations and the possible 
improvements regards to the issues are demonstrated below.

-   Because this is an observational study and there is no treatment involved, 
it would be hard to make causal inference, especially in a multilevel logistic 
regression.

-   The model is built under the assumption that patient visit data are kept at 
only 2 visits. It may be better to do a performance comparison using data that 
contains all the visits.

-   The method to deal with correlated variables should be considered more 
carefully. A PCA analysis may be useful to improve the performance of our model 
because we have several correlated variables.

## Reference

[1] "How Is Alzheimer's Disease Diagnosed?" National Institute on Aging, U.S. Department of Health and Human Services, <https://www.nia.nih.gov/health/how-alzheimers-disease-diagnosed>.

[2] Marcus, Daniel S, et al. "Open Access Series of Imaging Studies: Longitudinal MRI Data in Nondemented and Demented Older Adults." Journal of Cognitive Neuroscience, U.S. National Library of Medicine, Dec. 2010, <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2895005/>.

[3] "Oasis Brains." OASIS Brains - Open Access Series of Imaging Studies, <http://www.oasis-brains.org/#data>.

[4] “Home.” OARC Stats, https://stats.oarc.ucla.edu/r/dae/mixed-effects-logistic-regression/.

\newpage

## Appendix

**Dataset Additional Information**

This set consists of a longitudinal collection of 150 subjects aged 60 to 96. 
Each subject was scanned on two or more visits, separated by at least one year 
for a total of 373 imaging sessions. For each subject, 3 or 4 individual 
T1-weighted MRI scans obtained in single scan sessions are included. The 
subjects are all right-handed and include both men and women. 72 of the subjects
were characterized as nondemented throughout the study. 64 of the included 
subjects were characterized as demented at the time of their initial visits and 
remained so for subsequent scans, including 51 individuals with mild to moderate
Alzheimer's disease. Another 14 subjects were characterized as nondemented at 
the time of their initial visit and were subsequently characterized as demented 
at a later visit.

**Univariate Analysis**

```{r, echo=FALSE, fig.height=4, fig.width=6, fig.cap = "Figure 1. Variable Distributions Plot"}
# numeric variable
dens.age <- ggplot(patients) + aes(x=Age) + geom_density(lwd = 1.2, linetype = 1, alpha = 0.5,fill = "darkred")+geom_histogram(aes(y=after_stat(density)), bins = 30, fill =  "darkred")
dens.eTIV <- ggplot(data = patients, aes(x = eTIV)) + geom_density(lwd = 1, linetype = 1, alpha = 0.5,fill = "palegreen")+geom_histogram(aes(y=after_stat(density)), bins = 30, fill = "palegreen")
dens.MMSE <- ggplot(data = patients, aes(x = MMSE)) + geom_density(lwd = 1.2, linetype = 1, alpha = 0.5,fill = "yellow3")+geom_histogram(aes(y=after_stat(density)), bins = 30, fill = "yellow3")
dens.nWBV <- ggplot(data = patients, aes(x = nWBV)) + geom_density(lwd = 1.2, linetype = 1, alpha = 0.5,fill = "hotpink")+geom_histogram(aes(y=after_stat(density)), bins = 30, fill = "hotpink")
dens.ASF <- ggplot(data = patients, aes(x = ASF)) + geom_density(lwd = 1.2, linetype = 1, alpha = 0.5,fill = "cadetblue")+geom_histogram(aes(y=after_stat(density)), bins = 30, fill = "cadetblue")
dens.EDUC <- ggplot(data = patients, aes(x = EDUC)) + geom_density(lwd = 1.2, linetype = 1, alpha = 0.5,fill = "darkorange")+geom_histogram(aes(y=after_stat(density)), bins = 30, fill = "darkorange")
grid.arrange(dens.age, dens.eTIV, dens.MMSE, dens.nWBV, dens.ASF, dens.EDUC, ncol = 3)

```

**EDUC and SES**

```{r, fig.cap = "Figure 5. Relationship between EDUC and SES", echo=FALSE}
ggplot(data = p1) + 
  aes(x = EDUC, y = SES) + 
  geom_point() + 
  geom_smooth(formula = 'y ~ x', method = "lm") + 
  labs(titile = " Relationship between EDUC and SES", x = "Years of education", y = "Socioeconomic level")
```

**Converted Group Table**

```{r, warning = FALSE, message = FALSE, fig.cap= "Table 1. Converted Geoup Summary", echo=FALSE}
patients <- read_csv("oasis_longitudinal.csv")
summary.p <- summary(patients, maxsum = 7,
       digits = max(3, getOption("digits")-3))

# Response variable is CDR and convert it to factor (0 = Nondemented, 1 = Demented)
patients$Response<- ifelse(patients$CDR > 0, 1, 0)

# Rename the `M/F` column with `Gender`
patients <- patients %>% rename(Gender = `M/F`)

converted <- patients %>% filter(Group == "Converted") %>% count(Visit,CDR)
converted %>% kbl(caption = "Table 1. Vist and CDR Summary") %>%  kable_classic(position = "center", html_font = "Cambria")
```

**Model Summary**

```{r fig.cap= "Summary 1. summary of mod2", echo=FALSE}
# summary(mod2, 
#         pars = c("(Intercept)", "Age","MMSE","nWBV"),
#         probs = c(0.025, 0.975),
#         digits = 2)
print(mod2)
```


